Light inextensible strings under tension in the Schwarzschild geometry

### 2019-05-23 string_jpam.tex
comment out the properunits versions of the asymptotics
typo

 \begin{equation}\label{ell_properunits}
   \ell=\int_{r=1}^{r=1+w}ds
   =2\sqrt{w} + \frac{1}{3}w^{3/2} + O(w^{5/2})
 \end{equation}

@@

\begin{equation}\label{asymptotic_ell_properunits}
  \ell = w +  \frac{1}{2}\log w + \frac{1}{2} + \log(2)  +  \frac{1}{8}w^{-1} + O(w^{-2}),
\end{equation}

\begin{equation}\label{asymptotic_ell}
  \ell = 2GM\left(w +  \frac{1}{2}\log w + \frac{1}{2} + \log(2)  +  \frac{1}{8}w^{-1} + O(w^{-2})\right),
\end{equation}

@@

\begin{figure}[p] % Created by "light_closest_approach.R"
\centering
\includegraphics[width=170mm]{light_closest_approach.pdf}
\caption{Null geodesics in the Schwarzschild geometry, tangential
  at~$\phi=0$.  Note the differences between these curves and the taut
  strings shown elsewhere: unlike taug strings, null geodesics have
  positive curvature everywhere, may cross the event horizon inwards,
  and are never tangential to the event horizon}
\label{light_closest_approach}
\end{figure}

>>>>

%  \begin{equation}\label{ell_properunits}
%    \ell=\int_{r=1}^{r=1+w}ds
%    =2\sqrt{w} + \frac{1}{3}w^{3/2} + O(w^{5/2})
%  \end{equation}

@@

% \begin{equation}\label{asymptotic_ell_properunits}
%   \ell = w +  \frac{1}{2}\log w + \frac{1}{2} + \log(2)  +  \frac{1}{8}w^{-1} + O(w^{-2}),
% \end{equation}
% 
\begin{equation}\label{asymptotic_ell}
  \ell = 2GM\left(w +  \frac{1}{2}\log w + \frac{1}{2} + \log(2)  +  \frac{1}{8}w^{-1} + O(w^{-2})\right),
\end{equation}

@@

\begin{figure}[p] % Created by "light_closest_approach.R"
\centering
\includegraphics[width=170mm]{light_closest_approach.pdf}
\caption{Null geodesics in the Schwarzschild geometry, tangential
  at~$\phi=0$.  Note the differences between these curves and the taut
  strings shown elsewhere: unlike taut strings, null geodesics have
  positive curvature everywhere, may cross the event horizon inwards,
  and are never tangential to the event horizon}
\label{light_closest_approach}
\end{figure}
